Methods and Results

### 2022-10-06 ms.Rmd
Render updates

```{r, tables1, tab.cap = "Multi-level meta-regression model with log standard deviation (lnSD)"}
flextable(rbind(table_fixed,table_rand)) %>% 
      add_header_row(values = "Fixed Effects", colwidths = 3) %>% 
      bold(part = "header", i = 1) %>% 
      width(j = c(2,3,4), width = c(5, 2, 2)) %>%
      align(align = "center", part = "all") %>% 
      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects")))

>>>>

```{r, tables1,  tab.cap = "Multi-level meta-regression model with log standard deviation (lnSD)"}
flextable(rbind(table_fixed,table_rand)) %>% 
      add_header_row(values = "Fixed Effects", colwidths = 4) %>% 
      bold(part = "header", i = 1) %>% 
      width(j = c(2,3,4), width = c(5, 2, 2)) %>%
      align(align = "center", part = "all") %>% 
      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects"))) %>%

      autofit()
